Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-13 paper/sheaf_lics.tex
sheafification is a refl subu

As any separated type $T$ embeds in $\left(\Type_n^\modal\right)^T$,
it suffices to take the closure of $T$ to get a sheaf.

>>>>

As any separated type $T$ embeds in $\left(\Type_n^\modal\right)^T$,
it suffices to take the closure of $T$ to get a sheaf, and the unit
$\nu_T:T \to \star T$ is obvious.
\begin{prop}
  $(\star,\nu)$ defines a reflective subuniverse.
\end{prop}
\begin{proof}
  Let $T,Q:\Type_{n+1}$ such that $Q$ is a sheaf. Let $f:T\to Q$.
  Because $Q$ is a sheaf, it is in particular separated ; thus we can
  extend $f$ to $\square f:\square T\to Q$.

  But as $\star T$ is the closure of $\square T$, $\square T$ is dense
  into $\star T$, so the sheaf property of $Q$ allows to extend
  $\square f$ to $\star f:\star T \to Q$.

  As all these steps are universal, the composition is.
\end{proof}
